RadLib: a radiative property model library for CFD

### 2021-09-09 submissions/CPC_response_to_reviewers_revision2.md

# Response to Reviewers: CPC initial submission

Note, reviewer comments are included with responses in **bold** text.

## Reviewer 2

The authors have adequately addressed the reviewer's concern and significantly improved the quality of the manuscript
and the software. The reviewer recommends acceptance for publication.

**The authors thank the reviewer for their time and contributions.**

-------------------------------------

## Reviewer 3

The authors have responded to this reviewer's comments and have revised the manuscript substantially. There are still a
few issues that need to be resolved before it is accepted for publication.

**The authors thank the reviewer for their time and contributions.**

1) The capabilities and limitations of RadLib should be more clearly articulated. For example, different property models
   have different temperature ranges of applicability. While the authors specified what happens if the simulation
   temperature goes beyond the appropriate temperature range, they should comment or provide some recommendations on the
   appropriateness of the choice of the property model. For example, WSGG model has a valid temperature range of
   300-2400 K, and RadLib caps the absorption coefficient values at the respective bound if the simulation temperature
   is beyond this range. Can the authors provide some guidance on what is the error expected from such a strategy of
   allowing simulation to continue at ranges beyond the valid range of the property model? If the user knows that the
   simulation temperature is beyond 2400 K, is it recommended to use WSGG? Also, what is the applicable range of
   pressure in the models implemented? Related to this, on repeated readings, this reviewer felt a table to list the
   range of applicability for each model may be useful for understanding the capabilities of RadLib at-a-glance for an
   user.

   **Valid temperature ranges for the WSGG and RCSLW models were noted in their respective sections, and the applicable
   temperature range for the PM model has been added to its section. Additionally, the RCSLW model section specifies the
   range of pressures under which the RCSLW model can be applied. A table summarizing these conditions has been added to
   the beginning of Section 2.**

2) Please rephrase and, if possible, simplify the sentence on lines 82-86 ("Radiation property models, including those
   implemented in RadLib, are typically developed using ... correlations and modeling assumptions [4].") It is difficult
   to understand what exactly the authors are trying to convey in this sentence.

   **Sentence has been revised for clarity.**

3) Line 92 - 95: "Modern band models .. cant lose accuracy when applied to nonhomogeneous media and may still require
   large numbers of RTE evaluations [1]." Should this be "<can> lose accuracy when applied …"?

   **Yes, it should. Typo has been fixed.**

4) In Figure 2, Example S5: Do "n=2" "n=4", etc mean the number of bands in RCSLW? It needs to be clarified.
   Furthermore, can the authors comment on the physical significance of RCSLW n =1 and how is this different from PM
   which uses a spectral average value?

   **The figure's caption has been updated to clarify this. The main difference between the PM model and RCSLW (or WSGG) with n=1 
is that the RCSLW model always considers one transparent gas (representing gaps in the absorption spectrum) in addition 
to some number of gray gases, whereas the PM model uses an average over the entire spectrum, gaps included. The "clear gas" 
concept is discussed on page 4 during the derivation of the gray gas spectral RTE (Eq. 5), but the PM model description 
did not indicate its deviation from this and has been revised to clarify that it does not consider a transparent gas in 
addition to its single gray gas.**

5) In Figure 2: This is a kind of cosmetic request, but still if the legends and symbols can be made consistent it will
   be easier to read.

6) In lines 499-501: Please clarify the sentence, "The PM absorption coefficient is 27.4 atm−1 m−1 , which results in a
   calculated optical thicknesses of 0.09 and 0.36 m in the thick and thin layers, respectively." Optical thickness is a
   dimensionless quantity, it cannot be 0.36 m. The thicknesses of layers are changing in S2, so what do these 0.09 and
   0.36 refer to?

   **Those numbers are intended to be optical thicknesses and should not have units. This has been fixed. The layer thicknesses in 
Example S2 are physical lengths, as indicated.**

7) In Section 5.1, please clarify which files and functions belong to FDS and which to RadLib. For example, in line
   544, "This was done by editing the radi.f90 file." By looking at the f90 extension the readers can guess that
   radi.f90 is part of FDS and not RadLib. But then in the next sentence, there are references to A_WSGG and KAPPA_WSGG
   functions. Are these part of FDS?

   **Sentence has been revised to clarify which files and functions belong to FDS.**

8) In lines 562-564: "The FDS default model uses a single gray gas with a composition and temperature dependent
   absorption coefficient computed from RADCAL." Is this equivalent to the PM model in RadLib? If so, a comparison with
   PM from RadLib and FDS default will be a good validation. Also, what RTE solver does FDS default use?

   **No, they are not equivalent. FDS uses a finite-volume discrete ordinates RTE solver, as specified in the first paragraph of Section 5.1.**

9) In Section 5.2 can the author comment on the computational cost of RadLib-coupled FDS runs? Some quantitative
   information on the computational cost of using RadLib for a coupled run will be very useful. For example, the authors
   can compare the cost of the same FDS configuration simulated without any radiation, with RadLib, and with the
   FDS-default model.

10) Line 624: "At present, it includes three major radiation property models - Planck Mean (PM) absorption coefficients
    using the optically thin approximation, the weighted sum of gray gases (WSGG) model,..." PM can be used with any RTE
    solver in principle, not just with optically thin approximation. Is there any limitation within RadLib of using PM
    only with optically thin approximation?

   **This is an error; the reference to the optically thin approximation has been removed. It is true that the PM model can 
be used with any RTE solver. There is no limitation within RadLib that prevents its use with other RTE solvers.**

### 2021-09-13 manuscript/manuscript.tex
Grammar, usage, and proofreading edits for clarity in Sections 1, 2, and 2.1

        \begin{abstract}
            RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
        \end{abstract}

@@

    \begin{small}
        \noindent
        {\em Program Title:} RadLib                                         \\
        {\em CPC Library link to program files:} (to be added by Technical Editor) \\
        {\em Developer's repository link:} https://github.com/BYUignite/radlib \\
        {\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
        {\em Licensing provisions(please choose one):} MIT \\
        {\em Programming language:} C++, Fortran, Python \\
        {\em Nature of problem(approx. 50-250 words):} \\
        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a high degree of specialization due to its complexity and the challenges associated with implementation in existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
        {\em Solution method(approx. 50-250 words):}\\
        We present RadLib, an open-source C++ library of validated radiation property models that can be applied alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with a provided ray-tracing solver, and possibility for expansion to include additional radiation property models and interfaces.\\
        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
        The library is intended to be used in Linux-like terminal applications.
        \\

@@

    Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem. Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures \citep{Modest_2016}. Additionally, some late-stage flame phenomena, particularly soot behavior and flamesheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the RadLib library, which implements three radiation property models, with C++, Python, and Fortran interfaces, and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.

    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat transfer, radiation is governed by a set of integro-differential equations that depend on both direction and wavelength, known as the radiative transfer equations (RTE). Computational radiation solvers require two distinct but interconnected parts: (1) a solution approach for the radiative transfer equations (RTE) and (2) a radiative property model.
    Complexity, implementation, and computational costs of these two parts can vary widely, depending on the models chosen. The optically thin model for solution of the RTE is trivial, while the discrete ordinates model (DOM) and Reverse Monte Carlo Ray Tracing (RMCRC) model, among others, are significantly more involved. Similarly for radiation property models, which range from simple correlations for mean absorption coefficients, to gray gas models such as the weighted sum of gray gas model (WSGG), to the more advanced Spectral Line WSGG (SLW) family of model, to full line-by-line (LBL) treatment. In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation, but advanced property models, such as the Rank Correlated SLW (RCSLW), discussed here, are nontrivial models to understand, implement, and validate.
    RadLib addresses this second radiative property model part of radiation simulation by providing a set of implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

    For an absorbing, emitting, and non-scattering medium (considered here), the RTE for intensity $I$ at a specified wavenumber $\eta$ in unit direction $\mathbf{s}$ is described by
% 
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_general}
            \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
        \end{equation}
    \end{linenomath}
%
    where $I_{\eta}$ is the radiative spectral intensity, $I_{b,\eta}$ is the spectral blackbody radiative intensity
    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
    along direction $\mathbf{s}$.
    Solving the RTE requires information about the radiative properties of the materials and media in the system.
    Radiative property data typically takes the form of radiation absorption
    coefficients $\kappa$, which are provided by a radiation property model.
    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules, and depends
    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
    Radiation property models typically consist of correlations between radiative properties and high-resolution
    spectral databases, reducing the huge amount of spectral data and
    simplifying evaluation of radiation absorption coefficients \cite{Zhang_2002b}.

    The direct solution of the spectral RTE using so-called line-by-line calculations in which the RTE is solved for each
    individual spectral line is computationally prohibitive for most practical configurations and is used primarily for model
    validation. Some band models rely on estimated or averaged "line-of-sight" property values that cannot be directly
    incorporated into the RTE.

    Modern band models require high-resolution databases and reorder emission levels rather than averaging across sequential
    absorption bands, but these can lose accuracy when applied to nonhomogeneous media and may still require large numbers of
    RTE evaluations \citep{Modest_2016}.

    Global models are an important class of radiation property models that use spectrally-integrated radiation properties \cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over the fixed wavenumber ranges $\eta_j$ to obtain
%
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_wsgg}
            \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
        \end{equation}
    \end{linenomath}
%
    where $I_b$ is the blackbody intensity, $I_j$ is the radiative intensity in the region defined by gray gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
    \begin{linenomath}
        \begin{align}
            &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
            &\sum_j a_j = 1.
        \end{align}
    \end{linenomath}
%
    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray gases. Normally, an additional ``clear gas'', $j=0$, is included that represents transparent windows in the spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$ by summing the individual gray gas:
%
    \begin{linenomath}
        \begin{equation}
            I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
        \end{equation}
    \end{linenomath}
%

    The heat flux $\mathbf{q}$ (in units of kW/m$^2$) and volumetric radiative heat source $Q$ (kW/m$^3$) can be calculated by integrating over directional solid angles ($\mathbf{s}\Omega$) on the sphere and finding the divergence of the resulting vector field,
%
    \begin{linenomath}
        \begin{equation}
            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega.
        \end{equation}
    \end{linenomath}
%
    \begin{linenomath}
        \begin{equation}
            Q = -\nabla\cdot\mathbf{q}.
        \end{equation}
    \end{linenomath}
%
    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
    while limiting computational costs.

    With RadLib, we aim to provide researchers with a convenient access point for radiative property models that
    can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with optional
    Python and Fortran interfaces. RadLib calculates radiation absorption coefficients and weighting factors for use in global
    radiation models. Expansion to other radiative properties and model types is possible. Three models are fully implemented
    and validated.

@@

    At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption
    coefficients, most often applied alongside the optically thin approximation, a weighted sum of gray gases (WSGG)
    model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model. These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution spectral databases like RADCAL, HITRAN, and HITEMP \citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot. The property models implemented in RadLib apply only to non-scattering media.

    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
    which they apply.

    \begin{table}
        \caption{Summary of radiative property models in RadLib.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l}
                \hline
                Model & T range (K) & P range (atm) & Refs.   \\
                \hline
                PM      & 300\textendash 2500 & 1                   & \cite{TNF} \\
                WSGG    & 300\textendash 2400 & 1                   & \cite{Bordbar_2020,Bordbar_2014} \\
                RCSLW   & 300\textendash 3000 & 0.1\textendash 50   &  \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
    (with no transparent gas)
    and computes the absorption coefficient as a function of temperature, pressure, and gas composition.

    The particular version of the model implemented is from the Turbulent Nonpremixed Flames (TNF) workshop \cite{TNF}. This is a long-running collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been extensively researched for flame temperature, velocity, and composition profiles, and these serve as target flames for computational scientists to validate simulations and models. The PM model implemented here is the one advocated (and hence widely used) by the TNF workshop.

    For each species, the PM model provides the absorption coefficient as fourth or fifth order polynomial fits in one
    or two temperature ranges to $\kappa(T)$ values computed from the RADCAL database \cite{Grosshandler_1993}.
    Ultimately, the model accommodates temperatures between 300 K and 2500 K. See
    \cite{TNF} for details and references. The PM model here considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4}.
    The last two species have lower absorption than the first two, but are included because \ce{CH4} and syngas
    (consisting of \ce{CO} and \ce{H2}) are common fuels in combustion applications and so are present in the TNF flames
    in high concentrations in the fuel stream. (\ce{CO} is also a common species in rich flame regions and is also included in the RCSLW model.)

    The PM model is not as accurate as the other two models considered, and this is illustrated in Section~\ref{s:discussion}.
    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its relatively common use in some simulations.
    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100 K or more \cite{Frank_2000,Zhu_2002,Coelho_2002}, though this will depend strongly on the geometric configuration. Accurate results have been reported for hydrogen jet flames \cite{Barlow_1999}.

    The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation. Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss. It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%. At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.

@@

    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
%
    \begin{figure}
        \begin{center}
            \begin{tabular}{c c}
                Example S1                                      & Example S2 \\
                \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
                Example S3                                      & Example S4 \\
                \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
                Example S5                                      & Example B3 \\
                \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
            \end{tabular}
            \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
                refers to the number of gray gases considered.}
            \label{f:examples}
        \end{center}
    \end{figure}
%
    \begin{figure}
        \begin{center}
            \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
            \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
            \label{f:exSb1}
        \end{center}
    \end{figure}
%

>>>>

        \begin{abstract}
            RadLib is a C++ library of radiation property models that can be applied to a variety of systems involving
            radiative heat transfer, including CFD simulations. RadLib includes three major radiation property
            models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the
            rank-correlation spectral line-weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and
            Fortran interfaces and can be expanded to include additional models. Several example cases illustrate the
            use of the models with an included ray-tracing solver, compare their accuracy relative to
            line-by-line (LBL) solutions, and compare their computational costs. Finally, RadLib is coupled with Fire
            Dynamics Simulator (FDS) in an ethylene burner flame example case to demonstrate its use with existing
            CFD software. RadLib provides researchers with convenient access to validated radiation property models
            and a framework for further development.
        \end{abstract}

@@

    \begin{small}
        \noindent
        {\em Program Title:} RadLib                                         \\
        {\em CPC Library link to program files:} (to be added by Technical Editor) \\
        {\em Developer's repository link:} https://github.com/BYUignite/radlib \\
        {\em Code Ocean capsule:} https://codeocean.com/capsule/0997975/tree \\
        {\em Licensing provisions(please choose one):} MIT \\
        {\em Programming language:} C++, Fortran, Python \\
        {\em Nature of problem(approx. 50-250 words):} \\
        Radiative heat transfer in combustion CFD problems is typically neglected or oversimplified, resulting in
        significant error and inaccuracy in combustion simulations. Radiation modeling, however, often requires a
        high degree of specialization due to its complexity and the challenges associated with implementation in
        existing CFD codes, which presents a substantial obstacle to researchers who wish to address the inaccuracies
        introduced by insufficient radiative heat transfer modeling in combustion simulations. \\
        {\em Solution method(approx. 50-250 words):}\\
        We present RadLib, an open-source C++ library of validated radiation property models that can be applied
        alongside various RTE solution methods to ease some of the obstacles associated with radiation modeling for
        combustion CFD. The package includes C++, Fortran, and Python interfaces, several illustrative examples with
        a provided ray-tracing solver, and an integrated example using Fire Dynamics Simulator (FDS). RadLib can also
        be expanded to include additional radiative property models and interfaces. \\
        {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
        The RadLib library is intended to be used in Linux-like terminal applications.
        \\

@@

    Modeling radiative heat transfer in high temperature participating media systems is challenging, particularly in
    combustion systems.
    Combustion CFD is uniquely challenging because
    it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and
    radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction
    kinetics---that span many orders of magnitude in both length and time scales.
    Radiation modeling often complicates combustion simulations because accurate models can be difficult to
    implement and
    computationally expensive relative to overall simulation costs.
    Radiative heat transfer modeling in combustion systems
    is frequently neglected or oversimplified, resulting in significant flame temperature prediction errors~\citep{Modest_2016}.
    Additionally, some late-stage flame phenomena, particularly soot behavior and flame sheet breakthrough,
    increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate
    accurately without robust radiation modeling~\cite{Modest_2013}. These problems motivated development of the
    RadLib library, which implements three radiation property models with C++, Python, and Fortran interfaces and
    provides a framework for additional models and further development, providing researchers with convenient access to
    advanced radiation property modeling tools.

    The core mechanisms of radiative phenomena are physically and mathematically complex. Unlike other modes of heat
    transfer, radiation is governed by a set of directionally and spectrally dependent integro-differential equations
    known as the radiative transfer
    equations (RTEs). Computational radiation solvers require two distinct
    but interconnected parts: (1) a solution approach for the radiative transfer equations (RTEs) and (2) a radiative
    property model.
    The complexity, implementation, and computational costs of these two parts can vary widely depending on the models
    chosen. For example, the optically thin approximation for solution of the RTE is trivial, while the discrete
    ordinates model (DOM) and
    reverse Monte Carlo ray tracing (RMCRC) model, among others, are significantly more involved. Similarly,
    radiation property models range from simple correlations for computing mean absorption coefficients to gray gas
    models, including the weighted sum of gray gases (WSGG) model, to more advanced spectral
    line-weighted-sum-of-gray-gases (SLW) models to full line-by-line (LBL) treatment.
    In practical engineering simulations, solving the RTE is
    often the most complex and costly part of radiative simulation, but advanced property models such as the
    rank-correlated SLW (RCSLW) model, discussed in Section~\ref{s:RCSLW}, are nontrivial to understand, implement, and
    validate.
    RadLib addresses this second radiative property model part of radiation simulation by providing a set of
    implemented and validated radiation property models that can be applied to various solution approaches for the RTE.

    Consider an absorbing, emitting, and non-scattering medium. The RTE describes the radiative intensity $I$ at a
    specified wavenumber $\eta$ in unit direction $\mathbf{s}$ as
% 
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_general}
            \frac{dI_{\eta}}{ds} = -\kappa_{\eta}I_{\eta} + \kappa_{\eta}I_{b,\eta},
        \end{equation}
    \end{linenomath}
%
    where $I_{\eta}$ is the spectral radiative intensity, $I_{b,\eta}$ is the blackbody spectral radiative intensity
    (or Planck function), $\kappa_{\eta}$ is the spectral absorption coefficient of the medium, and $s$ is a path length
    along direction $\mathbf{s}$. Solving the RTE requires information about the radiative properties of the
    materials and media in the system. Radiative property data typically takes the form of radiation absorption
    coefficients $\kappa$, which are provided by a radiation property model.
    Gas absorption spectra consist of millions of spectral lines corresponding to the individual quantum mechanical energy levels of gas molecules and depend
    on the local thermochemical state of the system (e.g., temperature, pressure, and composition).
    Radiation property models typically consist of correlations between radiative properties and high-resolution
    spectral databases, reducing the huge amount of spectral data and
    simplifying evaluation of radiation absorption coefficients~\cite{Zhang_2002b}.

    The direct solution of the spectral RTE using so-called line-by-line (LBL) calculations---in which the RTE is solved
    for each individual spectral line---is computationally prohibitive for most practical configurations and used
    primarily for model validation. In contrast, simple ``band'' models rely on estimated or averaged ``line-of-sight''
    property values that cannot be directly incorporated into the RTE solution.
    Modern band models, which require access to high-resolution spectral databases, tend to reorder spectral emission
    levels rather than averaging across sequential absorption bands, but these can lose accuracy when applied to
    nonhomogeneous media and may still require large numbers of RTE evaluations~\citep{Modest_2016}.

    Global models are an important class of radiation property models that use spectrally-integrated radiation
    properties~\cite{Hottel_1967,Modest_2013,Modest_2016}. Assuming spectrally uniform (gray) properties over a
    wavenumber region $j$, we can integrate Eq.~\ref{e:RTE_general} over a set of fixed wavenumber ranges $\eta_j$ to
    obtain
%
    \begin{linenomath}
        \begin{equation}
            \label{e:RTE_wsgg}
            \frac{dI_j}{ds} = -\kappa_jI_j + a_j\kappa_jI_b, \hspace{20pt} j=0,1,...,n,
        \end{equation}
    \end{linenomath}
%
    where $I_b$ is the total blackbody intensity, $I_j$ is the total radiative intensity in the region defined by gray
    gas $j$, $\kappa_j$ is the spectrally integrated absorption coefficient for gray gas $j$, and $a_j$ is a weighting factor defined by
%
    \begin{linenomath}
        \begin{align}
            &a_j= \frac{\int_{\eta_j}I_{b,\eta}d\eta}{I_b},\\
            &\sum_j a_j = 1.
        \end{align}
    \end{linenomath}
%
    Given spatial profiles of $\kappa_j$ and $a_j$, Eq.~\ref{e:RTE_wsgg} can be evaluated for each of the $n$ gray
    gases. Normally, an additional ``clear gas'', $j=0$, is included to represent transparent windows in the
    spectrum for which $\kappa_0=0$. This gray gas approach allows calculation of the total radiative intensity $I$
    by summing the individual gray gas intensities:
%
    \begin{linenomath}
        \begin{equation}
            I=\int_{\eta=0}^{\infty}I_{\eta}d\eta=\sum_{j=1}^n I_j.
        \end{equation}
    \end{linenomath}
%
    The heat flux $\mathbf{q}$ (kW/m$^2$) can be calculated by integrating over the directional solid
    angles $\mathbf{s}\Omega$ on the sphere, and the volumetric radiative heat source $Q$ (kW/m$^3$) can be found by
    computing the divergence of the resulting vector field:
%
    \begin{linenomath}
        \begin{equation}
            \mathbf{q} = \int_{4\pi}I(\mathbf{s})\mathbf{s}d\Omega,
        \end{equation}
    \end{linenomath}
%
    \begin{linenomath}
        \begin{equation}
            Q = -\nabla\cdot\mathbf{q}.
        \end{equation}
    \end{linenomath}
%
    Global models are especially attractive in computational heat transfer applications because they can provide good accuracy
    while limiting computational costs.

    RadLib calculates radiation absorption coefficients and weighting factors for use in global
    radiation models. It can interface with various RTE solution approaches suitable for CFD applications and serves
    as a convenient access point for radiative property modeling.
    The RadLib library includes three property models that are fully implemented
    and validated, but it can also be expanded to include other radiative properties and model types.

@@

    At present, RadLib includes three radiation property models of varying complexity: the Planck Mean (PM) absorption
    coefficients model, a weighted sum of gray gases (WSGG)
    model, and the rank-correlated spectral line-weighted-sum-of-gray-gases (RCSLW) model. These models were chosen
    for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

    Radiation absorption coefficients are typically calculated via correlations developed from high-resolution
    spectral databases like RADCAL, HITRAN, and HITEMP~\citep{Grosshandler_1993,Rothman_2010} that relate spectral line strength to properties such as temperature, pressure, and gas composition \citep{Zhang_2002b}. At present, RadLib considers up to four gas species (H$_2$O, CO, CO$_2$, and CH$_4$), depending on the model, and soot. The property models implemented in RadLib apply only to non-scattering media.
    Table~\ref{t:models} summarizes RadLib's three radiative property models and the thermodynamic conditions under
    which they apply.

    \begin{table}
        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
        applied.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l}
                \hline
                Model & T range & P range & Refs.   \\
                \hline
                PM      & 300\textendash 2500 K & 1 atm               & \cite{TNF} \\
                WSGG    & 300\textendash 2400 K & 1 atm               & \cite{Bordbar_2020,Bordbar_2014} \\
                RCSLW   & 300\textendash 3000 K & 0.1\textendash 50 atm &  \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}

@@

    The Planck Mean (PM) model is the simplest of the three models implemented. This model assumes a single gray gas
    (with no transparent gas)
    and computes the absorption coefficient as a function of temperature and gas composition.

    The particular version of the model implemented comes from the Turbulent Nonpremixed Flames (TNF)
    workshop~\cite{TNF}, a long-running collaboration between experimental and computational researchers in turbulent
    combustion~\citep{Smith_2003,Barlow_2001}. The workshop includes a number of laboratory jet flames that have been
    extensively characterized---including temperature, velocity, and composition profiles---and which serve as target
    flames for computational scientists validating simulations and models. The PM model implemented in RadLib is the
    one recommended by the TNF workshop and is widely used in turbulent combustion simulation research.

    For each gas species considered, the PM model provides the absorption coefficient $\kappa(T)$ as a fourth or fifth order
    polynomial fit in one of two temperature ranges to values computed from the RADCAL spetral database~\cite{Grosshandler_1993}.
    It considers the species \ce{CO2}, \ce{H2O}, \ce{CO}, and \ce{CH4} at temperatures between 300 K and 2500 K.
    \ce{CO} and \ce{CH4} contribute significantly less to radiative absorption and emission than \ce{CO2} and
    \ce{H2O} do, but are included here because of their strong presence in the TNF workshop flames, several of which
    use methane (\ce{CH4}) or syngas (mixture of \ce{CO} and \ce{H2}) fuels. For more details on the TNF workshop
    flames and the TNF radiation model, see \cite{TNF}.

    The PM model is not as accurate as the other two models considered; this is illustrated by the examples cases
    presented in Sections~\ref{s:Examples} and~\ref{s:discussion}.
    It is implemented in RadLib primarily for comparison and evaluation against other radiation property models
    because it is commonly used in combustion simulations.
    The model has been reported to overpredict radiative losses and underpredict flame temperature by as much as 100
    K or more~\cite{Frank_2000,Zhu_2002,Coelho_2002}, though this depends strongly on the simulation geometry. Accurate
    results have been reported for hydrogen jet flames~\cite{Barlow_1999}.

    The PM model is most often used in conjunction with the optically-thin approximation for solving the RTE; in this
    case, the radiative source term of the energy transport equation is particularly simple, and the overall
    computational cost of the radiative treatment is negligible compared to other aspects of reacting flow
    simulations. Many combustion applications with relatively low radiative heat loss can be considered optically
    thin with respect to radiation; non-sooting laboratory-scale research jet flames, for example, tend to experience
    radiative losses of about 5\%. In such cases, when radiative losses are relatively small, the accuracy of the
    radiative property model is not as crucial to simulation results, and simpler radiative treatments like the PM model
    may be appropriate.

@@

    Figures~\ref{f:examples} and~\ref{f:exSb1} display comparative results for the PM, WSGG, and RCSLW models implemented by RadLib in the example case configurations summarized in Table~\ref{t:examples}. These plots are included to demonstrate the examples that are provided with the code, and to compare the models to give an indication of their relative accuracy. In all examples, the RCSLW model data is computed using four gray gases ($n=4$) and one clear gas for consistent comparison to the WSGG model, with the exception of Example S5, in which the number of gray gases in the RCSLW model is varied. The RCSLW model is initialized using the mean temperature and composition on the domain for all cases except Example S5, which uses the maximum temperature.
%
    \begin{figure}
        \begin{center}
            \begin{tabular}{c c}
                Example S1                                      & Example S2 \\
                \includegraphics[width=2.75 in]{fig_ex_S1.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S2b.pdf} \\
                Example S3                                      & Example S4 \\
                \includegraphics[width=2.75 in]{fig_ex_S3a.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_S4a.pdf} \\
                Example S5                                      & Example B3 \\
                \includegraphics[width=2.75 in]{fig_ex_S5c.pdf} &
                \includegraphics[width=2.75 in]{fig_ex_B3.pdf}
            \end{tabular}
            \caption{Results for Examples S1-S5 and B3 summarized in Table~\ref{t:examples}. In Examples S2 and S5, $n$
                refers to the number of gray gases considered in the RCSLW model.}
            \label{f:examples}
        \end{center}
    \end{figure}
%
    \begin{figure}
        \begin{center}
            \includegraphics[width=5.5 in]{fig_ex_Sb1.pdf}
            \caption{Results for Example Sb1 summarized in Table~\ref{t:examples}.}
            \label{f:exSb1}
        \end{center}
    \end{figure}
%
